\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities
Updates: working on section 2 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic untill find the problem.

In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is shown in Section XXX. The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger will be. In addition, pressure differences %(eq.\ref{eq:pressure_dif}) 
acting on the interface will produce a net pressure force,

\begin{equation}
\Delta P= - \gamma \; \nabla \; \dot \; \hat{n} 
\label{eq:pressure_dif} 
\end{equation}

>>>>

In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is shown in Section \red{XXX}. The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is. In addition, pressure differences acting on the interface produces a net pressure force,      
\begin{equation}
\Delta P= - \gamma \; \nabla \; \dot \; \hat{n} 
\label{eq:pressure_dif} 
\end{equation}
